### 2022-03-19 paper/ase22/approach.tex
writing approach

\begin{description}
\item[{\bf G1}] the test suite should contain realistic sentences;
\item[{\bf G2}] the test suite should cover diverse syntactic structures;
  \item[{\bf G3}] each test case should be
categorized into a linguistic capability;
\item[{\bf G4}] the label of each test case should be
automatically and accurately defined.
\end{description}

\Chlst's templates generate complete and realistic sentences, and each
template maps to a linguistic capability, satisfying {\bf G1} and {\bf
  G3}. But \Chlst only uses \sw{X} manually created templates to
generate its test suite; all test cases generated by the same template
share the same syntactic structure, thus violating {\bf G2}. In
addition, the label of each \Chlst test case has to be decided
manually, associated with each template, violating {\bf G4}.

We present \tool{}, a new linguistic capability test case generation
tool, that satisfies all of these criteria.  \sw{I could not summarize
  a cohesive idea that drives our design. Leaving it here to fill in.
  Also, I felt my writing below still lacks justification for some
  design choices (e.g., why we do the differentiation).}
Figure~\ref{fig:overview} shows the overview of \tool{}, which
consists of two phases.  The \emph{specification-based seed
  generation} phase performs rule-based searches from a real-world
dataset ({\bf G1}) and template-based transformation to obtain the
initial seed sentences.  The search rules (e.g., search for neutral
sentences that do not include any positive or negative words) and
transformation templates (e.g., \sw{add an example} \jl{sentence
  negation}) are defined in the \emph{linguistic capability
  specifications}, which guarantee that each resulting seed conforms
to a specific linguistic capability ({\bf G3}) and is labelled
correctly ({\bf G4}).

The \emph{syntax-based sentence expansion} phase expands the seed
sentences with additional syntactic elements (i.e., words
\sw{more?}\jl{and production ruls in \cfg}) to cover many real-world
syntactic structures ({\bf G2}). It first performs a syntax analysis
to identify the part-of-speech (PoS) tags that can be inserted to each
seed, by comparing the PoS parse trees between the seed sentence and
many other sentences from a large reference dataset. Each identified
tag is inserted into the seed as a \emph{mask}. It then uses an NLP
recommendation model (i.e., BERT \cite{}) to suggest possible
words. If a resulting sentence is validated to be consistent with the
specification which additionally defines the rules for expansion
(e.g., the expanded word should be neutral), {\bf G3} and {\bf G4} are
still satisfied.  Last, because some validated sentences may include
unacceptable suggested words given the context \sw{is this the
  right motivation to do selection?} \jl{I edited the sentence. please
  let me know if it is clear}, we use a heuristic (i.e., the
confidence score from the NLP recommendation model) to select the more
realistic context-aware expanded sentences into \tool{}'s test suite.

@@

\subsection{Specification-based Seed Generation}
The seed generation phase of \tool starts by searching sentences in a
real-world dataset that match the rules defined in the linguistic
capability specification, and then transforming the matched sentences
using templates to generate seed sentences that conform to individual
linguistic capabilities. The reasons for this design choice are
twofold.  First, while generally judging which linguistic capability
any sentence falls into and which label it should have is infeasible,
there exist simple rules and templates to allow classifying the
resulting sentences into individual linguistic capabilities and with
the correct labels, with high confidence.  This enables us to test
each linguistic capability individually.  Second, searching from a
real-world dataset ensures that the sentences used as test cases for
testing linguistic capabilities are realistic and diverse. The diverse
test cases are more likely to achieve a high coverage of the target
model's functionality in each linguistic capability, thus detecting
more errors.

@@

Table \ref{tab:specification} shows the search rules and the
transformation templates of all 11 linguistic capabilities we
implemented in \tool{}. \sw{@Jaeseong: revise the rest of 3.1 based on
  Table \ref{tab:specification}. I commented out the old text but it
  is still in the tex file.}

@@

%\begin{figure}[t]
%  \centering
%  \lstinputlisting[language=json-pretty]{code/requirement_sa1.json}
%  \vspace{-10pt}
%  \caption{\SearchRequirementExampleFigCaption}
%  \vspace{-10pt}
%\end{figure}
%
%\begin{figure}[t]
%  \centering
%  \subfloat[][\TransformRequirementExampleSubFigCaption]{\lstinputlisting[language=json-pretty]{code/requirement_sa2.json}}
%  \\
%  \subfloat[][\TransformTemplateExampleSubFigCaption]{\lstinputlisting[language=python]{code/requirement_sa2.py}}
%  \\
%  \caption{\TransformRequirementExampleFigCaption}
%  \vspace{-10pt}
%\end{figure}
%
%Figure~\ref{fig:SearchReqEx} shows \lc of \SareqExOne. To evaluate
%this \lc, the input is required to be short and have only \neu \adjs,
%\neu \nns. In addition, the label needs to be \neu. Therefore, all
%short natural \sents with only \neu \adjs and \neu \nns are available
%to evaluate NLP models. In this work, the sentiment of the words for
%the search are classified based on the sentiment scores from
%\Swn~\cite{baccianella2010sentiwordnet}, a publicly available English
%sentiment lexicons.  It provides lexical sentiment scores and the
%sentiment word labels are categorized by implementing the rules
%in~\cite{mihaela2017sentiwordnetlabel}. Next, transform \req explains
%how the input and output needs to be tranfromed. Some \lc only accepts
%heavily limited input distribution, and it is unlikely to be included
%in searching dataset because of its high structural diversity, thus,
%finding such \sents is costly. Therefore, our approach is to find
%inputs by relaxing search requirement and transform the input to match
%the target requirement of the \lc. In this work, the inputs are
%transformed by word addition or perturbing the found inputs with \lc
%dependent templates. The figure~\ref{fig:TransformReqEx} shows the
%example of use of the template requirement. The \lc of \SareqExTwo in
%the figure~\ref{fig:TransformReqSubEx} requires inputs to be the
%negated \pstv \sents and the neutral expression in the middle. Rather
%than searching \sents that match the input distribution of the \lc,
%the \Model search \pstv and \neu inputs and combine them into negated
%\pstv \sents. Figure~\ref{fig:TransformTempSubEx} illustrates template
%for the \lc. According to the \lc, The value of ``sent1'' and
%``sent2'' become each searched \neu and \pstv inputs respectively, and
%the template completion generates new inputs that matches the target
%\lc. In addition, the transformation of inputs also produce high
%diversity in the inputs because of that from initially found
%inputs. In this paper, we will denote the searched inputs in this
%phase as seed inputs.

\subsection{Syntax-based Sentence Expansion}

The simple search rules and transformation templates used to generate
the seed sentences may limit the syntactic structures these seeds may
cover. To address this limitation, the syntax-based sentence expansion
phase extends the seed sentences to cover syntactic structures
commonly used in real-life sentences. Our idea is to differentiate the
parse trees between the seed sentences and the reference sentences
from a large real-world dataset. The extra PoS tags in the reference
parse trees are identified as potential syntactic elements for
expansion and inserted into the seed sentences as masks. We then use
masked language model to suggest the fill-ins. If the resulting
sentences still conform to the linguistic capability specification,
they are added to \tool{}'s test suite. \sw{May have some redundancy
  and inconsistency with the overview part.}

@@

Algorithm \ref{alg:diff} shows how masks are identified for each seed
sentence.  It takes the parse trees of the seeds, generated by the
Berkeley Neural
Parser~\cite{kitaev2018seedparser,kitaev2019seedparser}, and a
reference context-free grammar (CFG) from the Penn Treebank corpus
dataset \cite{} as inputs.  The reference CFG is learned from a large
dataset \cite{} that is representative of the distribution of
real-world language usage.  The algorithm identifies the discrepancy
between the seed syntax and the reference grammar to decide how a seed
can be expanded.
%This phase builds \pcfg from the reference corpus. \cfg
%is constructed by parsing sentences in the corpus and extracting
%\prodrs. In addition, the probability of \cfg is estimated by
%its frequency over corpus. The output of this phase is the constructed
%\pcfg, and it is compared with seed parse trees. For our
%implementation, we build the \pcfg from the Penn Treebank corpus dataset.

%\paragraph{Seed parsing.}
%To expand seed sentence and generate fluent and faithful sentence
%used for evaluation, \Model studies structure of each seed input for
%its expansion.
%Seed parsing takes each seed as
%input, and outputs its parse tree of the seed, using the Berkeley Neural
%Parser~\cite{kitaev2018seedparser,kitaev2019seedparser}.

%\paragraph{Reference parsing.}
%We take a large-scale real-world dataset as reference for sentence expansion.

@@

For each production of in each seed's parse tree (lines 3 and 4), we
extract its non-terminal at the left-hand-side (line 5), $s\_lhs$, and
the grammar symbols at the right-hand-side (line 6), $s\_rhs$. In line
7, the algorithm iterates through all productions in the reference
context-free grammar and match these that have the same non-terminal
at the left-hand-side as $s\_lhs$.  The right-hand-side of each
matched production is called $r\_rhs$.  If $s\_rhs$ consists of a
subset of the grammar symbols in $r\_rhs$ (line 8), the additional
symbols in the $r\_rhs$ are inserted as masks in the parse tree of
seed sentence, in their respective positions in the expanded
production.  The left to right traversal of the leaves of an expanded
parse tree forms a masked sentence.  Lastly, we randomly select $k$
masked sentences for the next sentence expansion and validation phase.
\sw{Add justification: why we need to select k masked sentences
  (performance?) and why random makes sense.}

\begin{figure*}[t]
  \centering
  \includegraphics[scale=0.7]{figs/running_example.pdf}
  \caption{\RunningExCaption}
%  Expansion of the seed sentence ``Or
%both.''. For a \prodr in seed ``NP->[DT]'' on the left, the \prodr of
%``NP->[DT, NNS]'' is found in reference. Thus, the component NNS can be expanded in the
%seed and ``NP->[DT]'' is replaced with ``NP->[DT, NNS]'' and it generates new
%expanded sentence on the right.
\end{figure*}

\paragraph{Running example.} Figure~\ref{fig:ExpEx} shows an example using Algorithm \ref{alg:diff}
to generate a masked sentence. The sentence ``Or both." is a seed of
\sw{which?} linguistic capability.  The tree on the left shows the
parse tree of this seed; it consists of two productions: ``FRAG->[CC,
  NP, .]" and ``NP->[DT]".  When matching the left-hand-side
non-terminal of the second production (i.e., ``NP") in the reference
CFG, we found that it includes a production ``NP->[DT, NNS]" which has
an additional symbol ``NNS" on the right-hand-side.  The algorithm
thus expands the parse tree with this symbol, shown in the second
tree.  The masked sentence ``Or both \{MASK\}." is the result of the
left-to-right traversal of this expanded parse tree.

%Given the seed parse tree and reference \pcfg, production
%differentiation phase suggests structural expansion candidates on the
%seed input. this phase aims to analyze which structural components and
%where they can be added into the seed structure for its expansion. To
%do so, we explore reference \prodrs comparing it with each \prodr used
%in seed input. This results in the phase described in
%Algorithm~\ref{code:ProdDiffAlg}. For each production rule in seed
%inputs ($seed\_prod$), it searches production rules in reference
%($ref\_prod$) which it has same non-terminal on the \lhs
%($seed\_prod.lhs==ref\_prod.lhs$) and superset of \rhs of the seed
%production rule ($seed\_prod.rhs \subset ref\_prod.rhs$).  As we
%assume that the reference \cfg is built from real world data
%distribution, the elements in the complement set ($ref\_prod.rhs -
%seed\_prod.rhs$) become an expansion candidate which can be expanded
%from the $seed\_prod.rhs$ found in real world. In addition, the
%measure of how consistent the production rule is with the given seed
%structure is given in its probability of the reference production rule
%($ref\_prob$) multiplied by that of parents of $seed\_prod$. The
%expansion candidate consists of terminal or nonterminal symbols. When
%there is a phrase-level or clause-level nonterminal symbol, \eg noun
%phrase, it needs to be expanded and replaced with word-level
%nonterminal or terminal symbols to generate the expansion
%candidate. The number of feasible replacement is unbounded because of
%its high degree of freedom. Therefore, in this work, we focus on the
%expansion candidate with only the word-level nonterminal or terminal
%symbols for the effectiveness of \Model. Lastly, the expanded
%component is replaced with the mask token for the next phase. The
%example of the expansion is illustrated in
%Figure~\ref{fig:ExpEx}. The ``NP->[DT]'' is queried into
%reference, and ``NP->[DT,NNS]'' is identified as its expansion
%candidate since the \rhs of ``NP->[DT,NNS]'' is superset of that of
%``NP->[DT]''. the component of NNS is replaced with mask token in
%sentence-level. Therefore, the ``Or both \{MASK\}.'' is suggested for
%the next phase.

\subsubsection{Sentence Expansion and Validation}

In this phase, the words to fill in the masks in the masked sentences
are suggested by the BERT pretrained model \cite{}.  The BERT model
suggests word for the mask symbol

according to its context \sw{what does context mean here?} around in
sentence.  \sw{Algorithm 1 does not require we only have one mask in
  the masked sentence. Can the model suggest multiple words at the
  same time?}  \sw{Say a bit more about the BERT model
  suggestion. E.g., it may suggest multiple words for the same mask
  but they are ranked?}

Because BERT model is not aware of the linguistic capability
specification and the grammar symbol in the expanded parse tree, an
expanded sentence using the suggested words may no longer satisfy the
linguistic capability specification. Therefore, we perform validation
on the suggested words and only accept them if the following three
criteria are met.

First, the PoS tag of the suggested word must match the PoS tag of the
expanded symbol in the parse tree. For the example in
Figure~\ref{fig:ExpEx}, the masked symbol is a ``NNS" (i.e., plural
noun); thus, the suggested word must also be a ``NNS". \sw{Say how we
  obtain the PoS tag of a suggested word.}  Second, we require that
the sentiment of the expanded sentence is the same as the seed
sentence. To ensure this, the suggested words must be neutral.
\sw{Should we present this as part of specification, called expansion
  rule?}  Third, we additionally verify that the expanded sentences
satisfied the same search rules for the seed sentence. Our goal for
generating the expanded sentences is to use them for evaluating the
\sa models on the associated \lc in addition to the seed sentence. It
is only achieved when the expanded sentences are also met with the
same search rules for the \lc. For LC1 as an example, the expanded
sentence must still conform to the specification of the seed's
linguistic capability specification. Therefore, the expanded sentences
are required to be short and to only have neutral adjectives and
nouns. \sw{Say why we use the third criteria only for LC1 and LC2.}
\jl{I added the explanation}

\paragraph{Running example.} The third step in Figure~\ref{fig:ExpEx} shows the words suggested
by BERT. For this masked sentence, BERT suggested six words. Each word
is associated with the confidence score provided by BERT, the PoS tag,
and the sentiment. Among the six words, only ``ways'' and ``things''
are validated by \tool{} because they have the Pos tag ``NNS'' and are
neutral. In addition, it is found that both sentences meets the search
rule of the associated \lc of \SareqExOne. In the end, two sentences
of ``Or both ways'' and ``Or both things'' are generated.  \sw{Do we
  also check if the expanded sentence meets the
  specification?}\jl{Yes. I added the explanation of validation of \lc
  \req}

%The suggested word are
%validated by three criteria. First, The tag of POS must be matched with
%that suggested from the production differentiation phase. In the
%example in the Figure~\ref{fig:ExpEx}, the mask token comes from the
%structural component of NNS, plural noun. Therefore, the BERT
%suggested words must be also tagged with the NNS. Accordingly, every
%words of the NNS are only available. Second, \Model focuses on the \sa
%task, and it assume that the suggested words must not change sentiment
%of its input and must preserve its consistency of original sentiment
%label. Therefore, we only accept the \neu words for the
%expansion. Third, the expanded sentences with the BERT suggested words
%must be appropriate for evaluating NLP models on the target \lc, and the
%sentences must pass the \req of the \lc. In this work, the BERT
%suggestions are validated by the three criteria.

\subsubsection{Sentence Selection}
\sw{@Jaeseong: Add how we select expanded sentences and motivate why.}
After 
\paragraph{Running example.} \sw{Refer to the example to say how we
  use the BERT score to select.} \jl{I dont think we need this
  subsection of sentence selection it is already explained at the
  previous stage with running example.}

>>>>

\begin{description}
\item[{\bf G1}] the test suite should contain realistic \sents;
\item[{\bf G2}] the test suite should cover diverse syntactic structures;
  \item[{\bf G3}] each test case should be
categorized into a \lc;
\item[{\bf G4}] the label of each test case should be
automatically and accurately defined.
\end{description}

\Chlst's templates generate complete and realistic \sents, and each
template maps to a \lc, satisfying {\bf G1} and {\bf
  G3}. But \Chlst only uses \sw{X} manually created templates to
generate its test suite; all test cases generated by the same template
share the same syntactic structure, thus violating {\bf G2}. In
addition, the label of each \Chlst test case has to be decided
manually, associated with each template, violating {\bf G4}.

We present \tool{}, a new \lc test case generation
tool, that satisfies all of these criteria.  \sw{I could not summarize
  a cohesive idea that drives our design. Leaving it here to fill in.
  Also, I felt my writing below still lacks justification for some
  design choices (e.g., why we do the differentiation).}
Figure~\ref{fig:overview} shows the overview of \tool{}, which
consists of two phases.  The \emph{specification-based seed
  generation} phase performs rule-based searches from a real-world
dataset ({\bf G1}) and template-based transformation to obtain the
initial seed \sents.  The search rules (e.g., search for \neu
\sents that do not include any \pstv or \ngtv words) and
transformation templates (e.g., \sw{add an example} \jl{\sent
  negation}) are defined in the \emph{\lc
  specifications}, which guarantee that each resulting seed conforms
to a specific \lc ({\bf G3}) and is labelled
correctly ({\bf G4}).

The \emph{syntax-based \sent expansion} phase expands the seed
\sents with additional syntactic elements (i.e., words
\sw{more?}\jl{and production ruls in \cfg}) to cover many real-world
syntactic structures ({\bf G2}). It first performs a syntax analysis
to identify the part-of-speech (PoS) tags that can be inserted to each
seed, by comparing the PoS parse trees between the seed \sent and
many other \sents from a large reference dataset. Each identified
tag is inserted into the seed as a \emph{mask}. It then uses an NLP
recommendation model (i.e., BERT \cite{}) to suggest possible
words. If a resulting \sent is validated to be consistent with the
specification which additionally defines the rules for expansion
(e.g., the expanded word should be \neu), {\bf G3} and {\bf G4} are
still satisfied.  Last, because some validated \sents may include
unacceptable suggested words given the context \sw{is this the
  right motivation to do selection?} \jl{I edited the \sent. please
  let me know if it is clear}, we use a heuristic (i.e., the
confidence score from the NLP recommendation model) to select the more
realistic context-aware expanded \sents into \tool{}'s test suite.

@@

\subsection{Specification-based Seed Generation}
The seed generation phase of \tool starts by searching \sents in a
real-world dataset that match the rules defined in the \lc
specification, and then transforming the matched \sents using
templates to generate seed \sents that conform to individual
\lcs. The reasons for this design choice are twofold.  First, while
generally judging which \lc any \sent falls into and which label it
should have is infeasible, there exist simple rules and templates to
allow classifying the resulting \sents into individual \lcs and
with the correct labels, with high confidence.  This enables us to
test each \lc individually.  Second, searching from a real-world
dataset ensures that the \sents used as test cases for testing \lcs
are realistic and diverse. The diverse test cases are more likely to
achieve a high coverage of the target model's functionality in each
\lc, thus detecting more errors.
%
In this phase, \tool first search and selects \sents applicable to
the \lc in a given real-world dataset with search rules. In case that
the search rules only fulfill portion of the \lc specifications, the
selected \sents are not yet appropriate to become seed, we
transform the selected \sents into seed \sents using the
heuristic templates.
%
Table~\ref{tab:specification} shows the search rules and the
transformation templates of all 11 linguistic capabilities we
implemented in \tool. The first column shows the \lc type and its
description, and the second column shows the search rule and
transformation template used in each \lc. For LC1 and LC2, the NLP
models are evaluated in the scope of short \sents with selective
sentiment words. It does not require any guidance for its
transformation because the search rule alone is sufficient to conform
to the \lcs. On the other hand, search rules of LC3 and LC4 are not is
not enough to match their \lc specification, thus \tool uses heuristic
templates to conform the found \sents to the \lc. For example, the
selected \sents becomes seeds by preturbing them with the templates
and by negating the selected demonstrative \sents to conform to LC3
and LC4 respectively (see the third and forth rows in
Table~\ref{tab:specification}).
\sw{@Jaeseong: revise the rest of 3.1 based on
  Table~\ref{tab:specification}. I commented out the old text but it
  is still in the tex file.} \jl{I revised and added the explanation}

@@

@@

%\begin{figure}[t]
%  \centering
%  \lstinputlisting[language=json-pretty]{code/requirement_sa1.json}
%  \vspace{-10pt}
%  \caption{\SearchRequirementExampleFigCaption}
%  \vspace{-10pt}
%\end{figure}
%
%\begin{figure}[t]
%  \centering
%  \subfloat[][\TransformRequirementExampleSubFigCaption]{\lstinputlisting[language=json-pretty]{code/requirement_sa2.json}}
%  \\
%  \subfloat[][\TransformTemplateExampleSubFigCaption]{\lstinputlisting[language=python]{code/requirement_sa2.py}}
%  \\
%  \caption{\TransformRequirementExampleFigCaption}
%  \vspace{-10pt}
%\end{figure}
%
%Figure~\ref{fig:SearchReqEx} shows \lc of \SareqExOne. To evaluate
%this \lc, the input is required to be short and have only \neu \adjs,
%\neu \nns. In addition, the label needs to be \neu. Therefore, all
%short natural \sents with only \neu \adjs and \neu \nns are available
%to evaluate NLP models. In this work, the sentiment of the words for
%the search are classified based on the sentiment scores from
%\Swn~\cite{baccianella2010sentiwordnet}, a publicly available English
%sentiment lexicons.  It provides lexical sentiment scores and the
%sentiment word labels are categorized by implementing the rules
%in~\cite{mihaela2017sentiwordnetlabel}. Next, transform \req explains
%how the input and output needs to be tranfromed. Some \lc only accepts
%heavily limited input distribution, and it is unlikely to be included
%in searching dataset because of its high structural diversity, thus,
%finding such \sents is costly. Therefore, our approach is to find
%inputs by relaxing search requirement and transform the input to match
%the target requirement of the \lc. In this work, the inputs are
%transformed by word addition or perturbing the found inputs with \lc
%dependent templates. The figure~\ref{fig:TransformReqEx} shows the
%example of use of the template requirement. The \lc of \SareqExTwo in
%the figure~\ref{fig:TransformReqSubEx} requires inputs to be the
%negated \pstv \sents and the \neu expression in the middle. Rather
%than searching \sents that match the input distribution of the \lc,
%the \Model search \pstv and \neu inputs and combine them into negated
%\pstv \sents. Figure~\ref{fig:TransformTempSubEx} illustrates template
%for the \lc. According to the \lc, The value of ``sent1'' and
%``sent2'' become each searched \neu and \pstv inputs respectively, and
%the template completion generates new inputs that matches the target
%\lc. In addition, the transformation of inputs also produce high
%diversity in the inputs because of that from initially found
%inputs. In this paper, we will denote the searched inputs in this
%phase as seed inputs.

\subsection{Syntax-based \Sent Expansion}

The simple search rules and transformation templates used to generate
the seed \sents may limit the syntactic structures these seeds may
cover. To address this limitation, the syntax-based \sent expansion
phase extends the seed \sents to cover syntactic structures
commonly used in real-life \sents. Our idea is to differentiate the
parse trees between the seed \sents and the reference \sents
from a large real-world dataset. The extra PoS tags in the reference
parse trees are identified as potential syntactic elements for
expansion and inserted into the seed \sents as masks. We then use
masked language model to suggest the fill-ins. If the resulting
\sents still conform to the \lc specification,
they are added to \tool{}'s test suite. \sw{May have some redundancy
  and inconsistency with the overview part.}

@@

Algorithm \ref{alg:diff} shows how masks are identified for each seed
\sent.  It takes the parse trees of the seeds, generated by the
Berkeley Neural
Parser~\cite{kitaev2018seedparser,kitaev2019seedparser}, and a
reference context-free grammar (CFG) from the Penn Treebank corpus
dataset \cite{} as inputs.  The reference CFG is learned from a large
dataset \cite{} that is representative of the distribution of
real-world language usage.  The algorithm identifies the discrepancy
between the seed syntax and the reference grammar to decide how a seed
can be expanded.
%This phase builds \pcfg from the reference corpus. \cfg
%is constructed by parsing \sents in the corpus and extracting
%\prodrs. In addition, the probability of \cfg is estimated by
%its frequency over corpus. The output of this phase is the constructed
%\pcfg, and it is compared with seed parse trees. For our
%implementation, we build the \pcfg from the Penn Treebank corpus dataset.

%\paragraph{Seed parsing.}
%To expand seed \sent and generate fluent and faithful \sent
%used for evaluation, \Model studies structure of each seed input for
%its expansion.
%Seed parsing takes each seed as
%input, and outputs its parse tree of the seed, using the Berkeley Neural
%Parser~\cite{kitaev2018seedparser,kitaev2019seedparser}.

%\paragraph{Reference parsing.}
%We take a large-scale real-world dataset as reference for \sent expansion.

@@

For each production of in each seed's parse tree (lines 3 and 4), we
extract its non-terminal at the left-hand-side (line 5), $s\_lhs$, and
the grammar symbols at the right-hand-side (line 6), $s\_rhs$. In line
7, the algorithm iterates through all productions in the reference
context-free grammar and match these that have the same non-terminal
at the left-hand-side as $s\_lhs$.  The right-hand-side of each
matched production is called $r\_rhs$.  If $s\_rhs$ consists of a
subset of the grammar symbols in $r\_rhs$ (line 8), the additional
symbols in the $r\_rhs$ are inserted as masks in the parse tree of
seed \sent, in their respective positions in the expanded
production.  The left to right traversal of the leaves of an expanded
parse tree forms a masked \sent.  Lastly, we randomly select $k$
masked \sents for the next \sent expansion and validation phase.
\sw{Add justification: why we need to select k masked \sents
  (performance?) and why random makes sense.}

\begin{figure*}[t]
  \centering
  \includegraphics[scale=0.7]{figs/running_example.pdf}
  \caption{\RunningExCaption}
%  Expansion of the seed \sent ``Or
%both.''. For a \prodr in seed ``NP->[DT]'' on the left, the \prodr of
%``NP->[DT, NNS]'' is found in reference. Thus, the component NNS can be expanded in the
%seed and ``NP->[DT]'' is replaced with ``NP->[DT, NNS]'' and it generates new
%expanded \sent on the right.
\end{figure*}

\paragraph{Running example.} Figure~\ref{fig:ExpEx} shows an example using Algorithm \ref{alg:diff}
to generate a masked \sent. The \sent ``Or both." is a seed of
\sw{which?} \lc.  The tree on the left shows the
parse tree of this seed; it consists of two productions: ``FRAG->[CC,
  NP, .]" and ``NP->[DT]".  When matching the left-hand-side
non-terminal of the second production (i.e., ``NP") in the reference
CFG, we found that it includes a production ``NP->[DT, NNS]" which has
an additional symbol ``NNS" on the right-hand-side.  The algorithm
thus expands the parse tree with this symbol, shown in the second
tree.  The masked \sent ``Or both \{MASK\}." is the result of the
left-to-right traversal of this expanded parse tree.

%Given the seed parse tree and reference \pcfg, production
%differentiation phase suggests structural expansion candidates on the
%seed input. this phase aims to analyze which structural components and
%where they can be added into the seed structure for its expansion. To
%do so, we explore reference \prodrs comparing it with each \prodr used
%in seed input. This results in the phase described in
%Algorithm~\ref{code:ProdDiffAlg}. For each production rule in seed
%inputs ($seed\_prod$), it searches production rules in reference
%($ref\_prod$) which it has same non-terminal on the \lhs
%($seed\_prod.lhs==ref\_prod.lhs$) and superset of \rhs of the seed
%production rule ($seed\_prod.rhs \subset ref\_prod.rhs$).  As we
%assume that the reference \cfg is built from real world data
%distribution, the elements in the complement set ($ref\_prod.rhs -
%seed\_prod.rhs$) become an expansion candidate which can be expanded
%from the $seed\_prod.rhs$ found in real world. In addition, the
%measure of how consistent the production rule is with the given seed
%structure is given in its probability of the reference production rule
%($ref\_prob$) multiplied by that of parents of $seed\_prod$. The
%expansion candidate consists of terminal or nonterminal symbols. When
%there is a phrase-level or clause-level nonterminal symbol, \eg noun
%phrase, it needs to be expanded and replaced with word-level
%nonterminal or terminal symbols to generate the expansion
%candidate. The number of feasible replacement is unbounded because of
%its high degree of freedom. Therefore, in this work, we focus on the
%expansion candidate with only the word-level nonterminal or terminal
%symbols for the effectiveness of \Model. Lastly, the expanded
%component is replaced with the mask token for the next phase. The
%example of the expansion is illustrated in
%Figure~\ref{fig:ExpEx}. The ``NP->[DT]'' is queried into
%reference, and ``NP->[DT,NNS]'' is identified as its expansion
%candidate since the \rhs of ``NP->[DT,NNS]'' is superset of that of
%``NP->[DT]''. the component of NNS is replaced with mask token in
%\sent-level. Therefore, the ``Or both \{MASK\}.'' is suggested for
%the next phase.

\subsubsection{\Sent Expansion and Validation}

In this phase, the words to fill in the masks in the masked \sents
are suggested by the BERT pretrained model \cite{}.  The BERT model
suggests word for the mask symbol

according to its context \sw{what does context mean here?} around in
\sent.  \sw{Algorithm 1 does not require we only have one mask in
  the masked \sent. Can the model suggest multiple words at the
  same time?}  \sw{Say a bit more about the BERT model
  suggestion. E.g., it may suggest multiple words for the same mask
  but they are ranked?}

Because BERT model is not aware of the \lc
specification and the grammar symbol in the expanded parse tree, an
expanded \sent using the suggested words may no longer satisfy the
\lc specification. Therefore, we perform validation
on the suggested words and only accept them if the following three
criteria are met.

First, the PoS tag of the suggested word must match the PoS tag of the
expanded symbol in the parse tree. For the example in
Figure~\ref{fig:ExpEx}, the masked symbol is a ``NNS" (i.e., plural
noun); thus, the suggested word must also be a ``NNS". \sw{Say how we
  obtain the PoS tag of a suggested word.}  Second, we require that
the sentiment of the expanded \sent is the same as the seed
\sent. To ensure this, the suggested words must be \neu.
\sw{Should we present this as part of specification, called expansion
  rule?}  Third, we additionally verify that the expanded \sents
satisfied the same search rules for the seed \sent. Our goal for
generating the expanded \sents is to use them for evaluating the
\sa models on the associated \lc in addition to the seed \sent. It
is only achieved when the expanded \sents are also met with the
same search rules for the \lc. For LC1 as an example, the expanded
\sent must still conform to the specification of the seed's \lc
specification. Therefore, the expanded \sents are required to be
short and to only have \neu adjectives and \nns. \sw{Say why we use
  the third criteria only for LC1 and LC2.}  \jl{I added the
  explanation}

\paragraph{Running example.} The third step in Figure~\ref{fig:ExpEx} shows the words suggested
by BERT. For this masked \sent, BERT suggested six words. Each word
is associated with the confidence score provided by BERT, the PoS tag,
and the sentiment. Among the six words, only ``ways'' and ``things''
are validated by \tool{} because they have the Pos tag ``NNS'' and are
\neu. In addition, it is found that both \sents meets the search
rule of the associated \lc of \SareqExOne. In the end, two \sents
of ``Or both ways'' and ``Or both things'' are generated.  \sw{Do we
  also check if the expanded \sent meets the
  specification?}\jl{Yes. I added the explanation of validation of \lc
  \req}

%The suggested word are
%validated by three criteria. First, The tag of POS must be matched with
%that suggested from the production differentiation phase. In the
%example in the Figure~\ref{fig:ExpEx}, the mask token comes from the
%structural component of NNS, plural noun. Therefore, the BERT
%suggested words must be also tagged with the NNS. Accordingly, every
%words of the NNS are only available. Second, \Model focuses on the \sa
%task, and it assume that the suggested words must not change sentiment
%of its input and must preserve its consistency of original sentiment
%label. Therefore, we only accept the \neu words for the
%expansion. Third, the expanded \sents with the BERT suggested words
%must be appropriate for evaluating NLP models on the target \lc, and the
%\sents must pass the \req of the \lc. In this work, the BERT
%suggestions are validated by the three criteria.

\subsubsection{\Sent Selection}
\sw{@Jaeseong: Add how we select expanded \sents and motivate why.}
After 
\paragraph{Running example.} \sw{Refer to the example to say how we
  use the BERT score to select.} \jl{I dont think we need this
  subsection of \sent selection it is already explained at the
  previous stage with running example.}
